---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fiodata

<!-- badges: start -->
[![R-CMD-check](https://github.com/albersonmiranda/fiodata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/albersonmiranda/fiodata/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/fiodata)](https://CRAN.R-project.org/package=fiodata)
[![Downloads](https://cranlogs.r-pkg.org/badges/grand-total/fiodata)](https://CRAN.R-project.org/package=fiodata)
<!-- badges: end -->

{fiodata} is a data-only package containing input-output matrices for R. It serves as a companion to the [{fio}](https://github.com/albersonmiranda/fio) package, providing the necessary data for input-output analysis while keeping the main package size manageable.

## Datasets

The package currently includes two major datasets provided by the Center for Computational Studies in General Equilibrium (CECEG) at the Federal University of Espírito Santo (UFES):

*   `br_2020`: Brazilian input-output matrix for the year 2020, featuring 51 sectors.
*   `world_2000`: World input-output matrix for the year 2000, covering 26 countries and 23 sectors.

Both datasets are provided as R6 objects, allowing for easy access to various components such as intermediate transactions, total production, final demand, and more.

## Installation

You can install {fiodata} from CRAN with:

``` r
install.packages("fiodata")
```

## Example

Here is how you can load the data and explore its structure:

```{r example}
library(fiodata)

# Accessing the Brazilian 2020 matrix
br_2020

# Viewing the names of the available matrices within the object
names(br_2020)
```

For performing analysis on these matrices, please refer to the [{fio}](https://github.com/albersonmiranda/fio) package.
